`SimSurvey`: an `R` package to optimize the design and analysis of fisheries surveys by simulating spatially-correlated fish stocks

### 2019-09-24 analysis/paper/cover_letter.Rmd
Edit cover letter given Greg's suggestions

I am writing to submit our manuscript entitled, **"`SimSurvey`: an `R` package to optimize the design and analysis of fisheries surveys by simulating spatially-correlated fish stocks"**, for consideration as a **Research Article** in **PLOS ONE**. In our manuscript we introduce the `R` package **`SimSurvey`**, which has been designed to simplify the process of simulating surveys of age-structured and spatially-distributed fish populations. We believe our work to be a valuable contribution to the scientific literature as few tools have been built to facilitate simulation tests of the design and analysis of costly fishery independent surveys. Such surveys have become an integral part of the population monitoring programs led by many fisheries organizations and, as with any other monitoring program, good survey design and analysis is a critical prerequisite for obtaining reliable results. It has long been recognized that simulations are a useful tool for optimizing such surveys and, as such, several frameworks have been proposed and applied to try and answer the common question of "how much sampling is enough?"(e.g. Schnute and Haigh,  Canadian Journal of Fisheries and Aquatic Sciences, 2003). The **`SimSurvey`** package builds upon previous frameworks but extends the accessibility of the underlying simulation by wrapping it in an open-source `R` package.

>>>>

I am writing to submit our manuscript entitled, **"`SimSurvey`: an `R` package to optimize the design and analysis of fisheries surveys by simulating spatially-correlated fish stocks"**, for consideration as a **Research Article** in **PLOS ONE**. In our manuscript we introduce the `R` package **`SimSurvey`**, which has been designed to allow the process of simulating surveys of complex age-structured and spatially-correlated fish populations. We believe our work to be a valuable contribution to the scientific literature as few tools have been built to facilitate simulation tests of the design and analysis of costly fishery independent surveys. Such surveys have become an integral part of the population monitoring programs led by many fisheries organizations and, as with any other monitoring program, good survey design and analysis is a critical prerequisite for obtaining reliable results. It has long been recognized that simulations are a useful tool for optimizing such surveys and, as such, several frameworks have been proposed and applied to try and answer the common question of "how much sampling is enough?"(e.g. Schnute and Haigh,  Canadian Journal of Fisheries and Aquatic Sciences, 2003). The **`SimSurvey`** package builds upon previous frameworks by increasing the complexity of the simulated population to reflect the dynamic structure seen in fish populations and extends the accessibility of the underlying simulation by wrapping it in an open-source `R` package.
